Supplementary Material

### 2025-10-08 manuscript.tex
adjust manuscript and supplemental material

% In this section, we fit the QGP model to quantile forecasts from the 2023-24 CDC flu forecasting competition. 
% Doing this allows for tools to be used to compare forecast performance between models and build ensemble forecasts beyond what is possible using only quantile forecasts \cite[]{mathis2024evaluation,wadsworth2023mixture}.  
In this section, the QGP and other models are 
used for QM of quantile forecasts targeting 
US flu hospitalizations. Beginning in 2013, the CDC began hosting a yearly 
forecast competition of the influenza outbreak in the US. This competition is 
known as FluSight. The flu epidemic typically begins in the fall and ends in 
late spring the following year, and the forecast competition lasts around 30 
weeks starting in October and ending in May. FluSight involves several academic 
and industry research teams who each independently develop forecasts  every 
week for predicting certain flu targets for future weeks 
\cite[]{biggerstaff2016results}. During the 2022-23 and 2023-24 seasons, the 
forecast targets were the 1, 2, 3, and 4-week ahead hospitalizations as 
reported by Health and Human Services (HHS) for the 50 US states, Puerto Rico, 
the District of Columbia, and the nation as a whole. The data for weekly 
hospitalizations of flu patients may be found at \cite{healthdata2024covidts}. 
The official guidelines of the most 2023-24 FluSight and all submitted quantile 
forecasts are publicly available at \cite{mathis2023flusight} 
\cite[]{mathis2024evaluation}.

Participating teams were free to create forecasts however they pleased, but 
forecasts for each target were required to consist of 23 quantiles for the 
probability levels 
$\boldsymbol{p} =(0.01, 0.025, 0.5, 0.1, ..., 0.95, 0.975, 0.99)$, 
which were given by FluSight. Figure \ref{fig:quant_forcs_us} shows examples 
of quantile forecasts of the same target from 12 participating teams. Each plot 
shows the log forecast for hospitalizations in the US for the week of 
January 13, 2024, and it is clear that there are major distributional 
differences between forecasts.
We denote a quantile forecast for flu hospitalizations as 
$\hat{Q}^{(H)}(\boldsymbol{p}) = (\hat{Q}^{(H)}(0.01), ..., \hat{Q}^{(H)}(0.99))$. 
The general quantile forecast representation format allowed for forecasts to be 
compared by the same metric, the weighted interval score (WIS), and to be 
easily combined into a multi-model ensemble forecast 
\cite[]{mathis2024evaluation}. However, under the quantile representation, 
the tools for scoring forecasts and for building ensemble models are limited 
as many of the existing tools for scoring forecasts and constructing ensembles 
require CDFs or PDFs \cite[]{wadsworth2023mixture,ranjan2010combining}. 
Because of these limitations, it may be desirable to approximate continuous 
distributions from the quantile forecasts to allow for more flexibility in 
scoring or ensemble building. In this section, we fit the QGP model for QM to 
every forecast of hospitalizations submitted to the FluSight during the 2023-24 
season, and an analysis is made to compare the scoring of the quantile 
forecasts to QGP estimated forecasts using proper scoring rules.

@@

Before fitting a QGP model to a quantile forecast we transformed the quantiles 
$\hat{Q}^{(H)}(\boldsymbol{p})$ to $\text{log}(\hat{Q}^{(H)}(\boldsymbol{p}) + 1)$ 
so that forecasts for all states were on a similar scale. The model fit was 
the same as the QGP fit in section \ref{sec:uk_matching}, including the same 
prior distribution assignments.
According to the official forecast competition rules, no forecast could include 
quantiles that were less than 0. As a result, there were forecasts with one or 
many quantiles equal to 0. When fitting the QGP model, these instances of 0 
values were removed so that some forecasts had $K < 23$ quantiles. Between 39 
competing forecast teams, 53 locations, 29 forecast dates, and 4 horizons, 
there were 180,312 quantile forecasts to which the QGP was fit. For each 
forecast, the WIS was calculated for the quantile forecast and the continuous 
ranked probability score (CRPS) was calculated over the predictive distribution 
of the fit QGP model.

@@

Figures \ref{fig:flu_horizon_corr} and \ref{fig:flu_rank_corr} show results of 
comparing the WIS from quantile forecasts and the CRPS from the QGP fitted 
forecasts. Figure \ref{fig:flu_horizon_corr} has in the $x$-axis the WIS and 
CRPS is in the $y$-axis. Each point is for one forecast for any participating 
team, season week, and state. The plot is faceted by horizon. Clearly the 
relationship between the quantile forecasts and the QGP forecasts are very 
close with high correlation near 0.9 for each horizon.

\begin{figure}[hbt!]
    \centering
    \makebox[\textwidth][c]{%
        \adjustbox{trim=0 0 0 0,clip}{\includegraphics[scale=.5]{Images/all_methods_cwcor.png}}%
    }
    \caption{Scatterplots of WIS and CRPS values for forecasts from 39 
    different teams for 2023-24 CDC flu forecast competition. The plots are 
    faceted by forecast horizon. Each point represents scores for a flu 
    forecast for one week during the season, one state, and one competing team. 
    Points are transparent to show where more scores tended to be. Overall 
    linear correlation is also given in the corner of each plot.}
    \label{fig:flu_horizon_corr}
\end{figure}

Figure \ref{fig:flu_rank_corr} shows the ranking of teams under the quantile 
forecasts' WIS vs. the QGP forecasts' CRPS. Here we say a team is considered 
the best performing by having the lowest score averaged across all season 
weeks, states, and horizons. The $x$-axis indicates where one of the 39 teams 
ranks by WIS and the $y$-axis where they rank by CRPS. If a block is on the 
diagonal line, the team's ranking was the same under the WIS as under the CRPS. 
The darkness of the block indicates how correlated that team's WIS is to the 
CRPS over the whole season. Of the 39 teams represented, 16 have the same 
ranking for both scores, and for over half of all teams the ranking difference 
between WIS and CRPS is within 3 positions. For most teams the linear 
correlation between WIS and CRPS is very high with only five teams having a 
correlation below 0.85.

\begin{figure}[hbt!]
    \centering
    \makebox[\textwidth][c]{%
        \adjustbox{trim=0 0 0 0,clip}{\includegraphics[scale=.45]{Images/all_methods_dists.png}}%
    }
    \caption{Blocks showing the overall season ranking of 39 competing forecast 
    teams for WIS ($x$-axis) and CRPS ($y$-axis). Blocks on the diagonal line 
    have the same ranking under both scores. Blocks are shaded to show 
    correlation between WIS and CRPS for all forecasts submitted by that team.}
    \label{fig:flu_rank_corr}
\end{figure}

The results in this section show the close relationship between the quantile 
forecasts of the CDC flu forecast competition and the more complete forecast 
distributions estimated via QGP. The implications of these results include 
being able to score forecasts according to scoring rules used for continuous 
distributions, including more problem specific rules, and being able to combine 
forecasts into an ensemble according to sums of CDFs or PDFs. Increased 
flexibility in scoring and ensemble construction could lead to improved 
decision making as problem specific evaluation becomes more accessible.

@@

In this paper we consider the situation where quantiles with known probability 
levels are given as data or is given to represent a distribution rather than 
raw data or a fully defined distribution. We review basic properties of QFs, 
sample quantiles, and resulting CLTs which motivate a new model, the QGP 
model, for matching a set of quantiles to a continuous distribution. The QGP 
model is assessed for parameter estimation and inference, distribution 
approximation, and it is compared with other QM methods found in the 
literature. The simulation studies show that the QGP model does well in 
estimating parameters and allows for accurate measurement of uncertainty. It 
provides a way to perform QM for distributions defined by CDFs as well as 
quantile distributions where the CDF is difficult to evaluate.
An application of the QGP for QM of quantile forecasts from the 2023-24 
FluSight project shows how QGP matched distributions are closely related to 
the original quantile forecasts in terms forecast performance among competing 
models. QGP forecasts, however, may be scored using a variety of scoring rules 
unavailable to quantile forecasts, and independent forecasts may be combined 
using methods made only for combining distributions by CDF or PDF functions. 
QGP has already been applied in chapter 4 of \cite{wadsworth2024quantile} who 
used the QGP predictive distributions fit in section \ref{sec:qm_analysis} to 
construct ensemble forecasts.

Approximating continuous distributions given only a set of estimated quantiles 
is not a new idea, but QGP provides a method of doing so while also accurately 
accounting for asymptotic uncertainty in estimated or predicted quantiles. The 
CLTs in this paper are limited to the case where the quantiles are estimated 
given a distribution sample, however similar results have been shown for the 
quantile regression case where quantiles are estimated in the presence of 
covariates \cite[]{kocherginsky2005practical, koenker1978regression}. These 
results could lead to additional QM modeling using the QGP model where 
covariates are given, and this may be more akin to the QM done by 
\cite{sgouropoulos2015matching}. 
Additional research for the QGP model may be in how the required distribution 
function is selected. Where a true model is unknown, we elected to model a 
distribution as a normal mixture distribution. Of course this has its limits, 
and using other non parametric functions, similar to 
\cite{gasthaus2019probabilistic}, may provide needed flexibility. As long as 
the selected function is continuous and once differentiable, the theory herein 
applies.

The application in this paper suggests QM being useful for forecast hubs.  
\cite{gerding2023evaluating} found QM a necessity in order to evaluate 
forecasts by a new scoring rule with COVID-19 specific applications. The extra 
work that comes with QM may or may not be worth the effort for any given 
forecast hub, but in some contexts it is something worth considering.

>>>>

% In this section, we fit the QGP model to quantile forecasts from the 2023-24 CDC flu forecasting competition. 
% Doing this allows for tools to be used to compare forecast performance between models and build ensemble forecasts beyond what is possible using only quantile forecasts \cite[]{mathis2024evaluation,wadsworth2023mixture}.  
In this section, the QGP and other models are 
used for QM of quantile forecasts targeting 
US flu hospitalizations. Beginning in 2013, the CDC began hosting a yearly 
forecast competition of the influenza outbreak in the US. This competition is 
known as FluSight. The flu epidemic typically begins in the fall and ends in 
late spring the following year, and the forecast competition lasts around 30 
weeks starting in October and ending in May. FluSight involves 
a few dozen academic 
and industry research teams who each independently develop forecasts every 
week for predicting certain flu targets for future weeks 
\cite[]{biggerstaff2016results}. During the 2022-23 and 2023-24 seasons, the 
forecast targets were the 1, 2, 3, and 4-week ahead hospitalizations as 
reported by Health and Human Services (HHS) for the 50 US states, Puerto Rico, 
the District of Columbia, and the nation as a whole. The data for weekly 
hospitalizations of flu patients may be found at \cite{healthdata2024covidts}. 
The official guidelines of the 2023-24 FluSight and all submitted quantile 
forecasts are publicly available at \cite{mathis2023flusight} 
\cite[]{mathis2024evaluation}.

Participating teams were free to create forecasts however they pleased, but 
forecasts for each target were required to consist of 23 quantiles for the 
probability levels 
$\boldsymbol{p} =(0.01, 0.025, 0.5, 0.1, ..., 0.95, 0.975, 0.99)$, 
which were given by FluSight. Figure \ref{fig:quant_forcs_us} shows examples 
of quantile forecasts of the same target from 12 participating teams. Each plot 
shows the log forecast for hospitalizations in the US for the week of 
January 13, 2024, and it is clear that there are major distributional 
differences between forecasts.
We denote a quantile forecast for flu hospitalizations as 
$\hat{Q}^{(H)}(\boldsymbol{p}) = (\hat{Q}^{(H)}(0.01), ..., \hat{Q}^{(H)}(0.99))$. 
The general quantile forecast representation format allowed for forecasts to be 
compared by the same metric, the weighted interval score (WIS), and to be 
easily combined into a multi-model ensemble forecast 
\cite[]{mathis2024evaluation}. However, under the quantile representation, 
the tools for scoring forecasts and for building ensemble models are limited 
as many of the existing tools for scoring forecasts and constructing ensembles 
require CDFs or PDFs \cite[]{wadsworth2023mixture,ranjan2010combining}. 
Because of these limitations, it may be desirable to approximate continuous 
distributions from the quantile forecasts to allow for more flexibility in 
scoring or ensemble building. In this section, we fit the QGP and other
models for QM to 
forcasts submitted to the FluSight during the 2023-24 
season, and an analysis is made to compare the fits.

@@

Before fitting a QGP model to a quantile forecast we transformed the quantiles 
$\hat{Q}^{(H)}(\boldsymbol{p})$ to $\text{log}(\hat{Q}^{(H)}(\boldsymbol{p}) + 1)$ 
so that forecasts for all states were on a similar scale. The model fit was 
the same as the QGP fit in section \ref{sec:uk_matching}, including the same 
prior distribution assignments.
According to the official forecast competition rules, no forecast could include 
quantiles that were less than 0. As a result, there were forecasts with one or 
many quantiles equal to 0. When fitting the QGP model, these instances of 0 
values were removed so that some forecasts had $K < 23$ quantiles. Between 39 
competing forecast teams, 53 locations, 29 forecast dates, and 4 horizons, 
there were 161,093 quantile forecasts on which QM was done.
For each 
forecast, the WIS was calculated for the quantile forecast and the continuous 
ranked probability score (CRPS) was calculated over the predictive distribution 
of the fit QGP model.

@@

Figures \ref{fig:flu_methods_corr} shows results of 
comparing the WIS from quantile forecasts and the CRPS from the 
fitted forecasts for QGP, ORD, IND, SPL, and KDE methods. 
The plots have in the $x$-axis the WIS and 
CRPS is in the $y$-axis. Each point is for one forecast for any participating 
team, season week, and state. Unsurprisingly, the correlation between the
QM CRPS and WIS is very highly correlated for each method. For all but the KDE
method, there is a tendency for some CRPS values to go above the $x = y$ line
suggesting the CRPS scores are enlarged due to the addition of distribution
tails. The CRPS scores for the IND method also go below the $x = y$ line 
suggesting that the method's fit may be simply be poorer than the other methods.
The slightly lower correlation for the QGP compared to ORD and IND may also be
a result of adding more uncertainty in the fitting of tail quantiles.

\begin{figure}[hbt!]
    \centering
    \makebox[\textwidth][c]{%
        \adjustbox{trim=0 0 0 0,clip}{\includegraphics[scale=.5]{Images/all_methods_cwcor.png}}%
    }
    \caption{Scatterplots of WIS and CRPS values for forecasts from 39 
    different teams for 2023-24 CDC flu forecast competition. Each plot
    is for a different QM method. Each point represents scores for a flu 
    forecast for one week during the season, one state, and one competing team. 
    Points are transparent to show where more scores tended to be. Overall 
    linear correlation is also given in the corner of each plot.}
    \label{fig:flu_methods_corr}
\end{figure}

We do not know the true distributions from which each quantile forecast was
made, but we can assess closeness of fit by measuring the difference between
the QM quantiles and the original forecast quantiles given the FluSight
probability values.
Figure \ref{fig:all_methods_dists} shows the average over week mean absolute
error (MAE) and mean sqaure error (MSE) between the the newly estimated 
QM quantiles and the original forecast quantiles. The MAE and MSE values for the
SPL method are 0 for every week because the estimated quantile functions are 
interpolations of the original forecasts. Besides the SPL, however, the QGP
appears to estimate quantiles that are the closest to the original forecast
quantiles. The aveage MAE for the QGP is smaller than for the remaining methods
for each week and the MSE is smaller for most weeks showing a robustness which
the other methods -- namely ORD and KDE -- may lack.

\begin{figure}[hbt!]
    \centering
    \makebox[\textwidth][c]{%
        \adjustbox{trim=0 0 0 0,clip}{\includegraphics[scale=.45]{Images/all_methods_dists.png}}%
    }
    \caption{Mean absolute error (MAE) and mean square error (MSE) over week
    for FluSight QM quantiles for each of QGP, ORD, IND, SPL, and KDE methods.}
\end{figure}

@@

In this paper we consider the situation where quantiles with known probability 
levels are given as data or the quantiles represent a distribution rather than 
raw data or a fully defined distribution. We review basic properties of QFs, 
sample quantiles, and resulting CLTs which motivate a new model, the QGP 
model, for matching a set of quantiles to a continuous distribution. The QGP 
model is assessed for parameter estimation and inference, distribution 
approximation, and it is compared with other QM methods found in the 
literature. The QGP provides explicit and easily interpretable uncertainty 
quantification of QM distributions, and generally outperforms the methods to 
which it is compared, sometimes with the exception of the ORD.
An added advantage, however, is that the QGP 
provides a way to perform QM for distributions defined by CDFs as well as 
quantile distributions where the CDF is difficult to evaluate.
An application of QM on quantile forecasts from the 2023-24 
FluSight project demonstrates that QM methods allow for the use of the CRPS
for scoring forecasts which is able to account for distribution tail 
uncertainty. 
QGP and other QM forecasts may be scored using a variety of scoring rules 
unavailable to quantile forecasts, and independent forecasts may be combined 
using methods made only for combining distributions by CDF or PDF functions. 
QGP has already been applied in chapter 4 of \cite{wadsworth2024quantile} who 
used the QGP predictive distributions fit in section \ref{sec:qm_analysis} to 
construct ensemble forecasts.
In the analysis, it is shown that the QGP may offer a more robust
fit to quantile distributions than other QM methods.

Approximating continuous distributions given only a set of estimated quantiles 
is not a new idea, but QGP provides a method of doing so while also accurately 
accounting for asymptotic uncertainty in estimated or predicted quantiles. The 
CLTs in this paper are limited to the case where the quantiles are estimated 
given a distribution sample, however similar results have been shown for the 
quantile regression case where quantiles are estimated in the presence of 
covariates \cite[]{kocherginsky2005practical, koenker1978regression}. These 
results could lead to additional QM modeling using the QGP model where 
covariates are given, and this may be more akin to the QM done by 
\cite{sgouropoulos2015matching}. 
Additional research for the QGP model may be in how the required distribution 
function is selected. Where a true model is unknown, we elected to model a 
distribution as a normal mixture distribution. Of course this has its limits, 
and using other non parametric functions, similar to 
\cite{gasthaus2019probabilistic}, may provide needed flexibility. As long as 
the selected function is continuous and once differentiable, the theory herein 
applies. 
The application in this paper suggests QM being useful for forecast hubs.  
\cite{gerding2023evaluating} found QM a necessity in order to evaluate 
forecasts by a new scoring rule with COVID-19 specific applications.

### 2025-10-08 supplemental.tex
adjust manuscript and supplemental material

%% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
%% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
\usepackage{amsmath,amsthm,amssymb,scrextend,mathtools}
\usepackage{hyperref}
\usepackage{newtxmath} %for making indicator function
\usepackage{booktabs}
% \RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,backref=page,backref=page]{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\Huge
\begin{center}
  Supplementary Material
\end{center}
\normalsize

The figures herein are supplementary to those in the main manuscript. Figure 
\ref{fig:norm_dens} shows examples of marginal
posterior densities for QM of quantiles for a normal distribution from the 
simulation study in section 4.1 in
the main manuscript. The parameter uncertainty of the QGP and ORD models are 
unsurprisingly similar in
most cases, and where they differ it is hard to say that one is estimating the 
true parameter better than the
other. The IND model on the other hand has tighter densities, and often the 
bulk of the posterior is far from
the true parameter.

\begin{figure}
\centering
  \includegraphics[width = 1.1\linewidth]{Images/norm_params_fit.png}
\caption{Density plots of posterior distribution samples for normal parameters 
by QM for QGP, ORD, and
IND models. QM was done on estimated quantiles from a normal distribution with 
mean 4 and standard
deviation 3.5. The posterior densities are for $\mu$ (top left), 
$\sigma$ (top right), and 
sample size n (bottom). Plots are
faceted by the sample size $n \in \{50, 150, 500, 1,000\}$ 
($y$-axis) and number of 
quantiles $K \in \{7, 15, 23\}$ ($x$-axis).
Vertical lines (black) show the value of the true parameter}
\label{fig:norm_dens}
\end{figure}

Figures \ref{fig:exp_dens} and \ref{fig:exp_cov_dists} are from a simulation 
study similar to that of section 4.1 
except that QM was performed on
quantiles estimated from draws from an exponential distribution with 
parameter $\lambda = 4$ rather than a normal distribution. 
The results in the study for the exponential distribution were similar 
to those for the normal
distribution.

\begin{figure}
\centering
  \includegraphics[width = 1.1\linewidth]{Images/exp_params_fit.png}
\caption{Density plots of posterior distribution samples for the exponential 
parameters by QM for QGP,
ORD, and IND models. QM was done on estimated quantiles from a exponential 
distribution with parameter
$\lambda = 4$. The posterior densities are for $\lambda$
(left) and sample size $n$ (right). 
Plots are faceted by true sample
size $n \in \{50, 150, 500, 1,000\}$ ($y$-axis) and number of quantiles 
$K \in \{7, 15, 23\}$ 
($x$-axis). Vertical lines (black)
show the value of the true parameter.}
\label{fig:exp_dens}
\end{figure}

@@

??Figures 11, 12, and 13 were referred to
in section 4.2 of the main manuscript.??

@@

\begin{figure}[hbt!]
\centering
  \includegraphics[]{Images/mix_comps.png}
\caption{Future caption}
\label{fig:mix_comps}
\end{figure}

% \begin{table}[hbt!]
% \footnotesize
% \centering
% \caption{UWD1}
% \begin{adjustbox}{center}
% \begin{tabular}{lcccccc|cccccc}
%  & \multicolumn{6}{c}{QGP} & \multicolumn{6}{c}{QGP-n} \\
% \cmidrule(lr){2-7} \cmidrule(lr){8-13}
% Components & 1 & 2 & 3 & 4 & 5 & 6 & 1 & 2 & 3 & 4 & 5 & 6 \\
% \midrule
% EV & 0.063 & 0.025 & 0.021 & 0.020 & 0.020 & 0.020 & 
%       0.064 & 0.025 & 0.021 & 0.021 & 0.020 & 0.020\\
% La & 0.044 & 0.022 & 0.020 & 0.020 & 0.020 & 0.020 & 
%       0.044 & 0.021 & 0.020 & 0.020 & 0.020 & 0.020 \\
% MIX & 0.107 & 0.018 & 0.019 & 0.019 & 0.019 & 0.019 & 
%       0.157 & 0.018 & 0.019 & 0.018 & 0.018 & 0.018
% \end{tabular}
% \end{adjustbox}
% \end{table}

\begin{table}[hbt!]
\footnotesize
\centering
\caption{UWD1}
\begin{adjustbox}{center}
\begin{tabular}{clcccccc|cccccc}
& & \multicolumn{6}{c}{QGP} & \multicolumn{6}{c}{QGP-n} \\
\cmidrule(lr){3-8} \cmidrule(lr){9-14}
& Components & 1 & 2 & 3 & 4 & 5 & 6 & 1 & 2 & 3 & 4 & 5 & 6 \\
\midrule
\multirow{3}{*}{UWD1} &
EV & 0.063 & 0.025 & 0.021 & 0.020 & 0.020 & 0.020 & 
      0.064 & 0.025 & 0.021 & 0.021 & 0.020 & 0.020\\
 & La & 0.044 & 0.022 & 0.020 & 0.020 & 0.020 & 0.020 & 
      0.044 & 0.021 & 0.020 & 0.020 & 0.020 & 0.020 \\
 & MIX & 0.107 & 0.018 & 0.019 & 0.019 & 0.019 & 0.019 & 
      0.157 & 0.018 & 0.019 & 0.018 & 0.018 & 0.018 \\
      \hline
\multirow{3}{*}{TV} &
EV & 0.127 & 0.053 & 0.047 & 0.047 & 0.048 & 0.049 &
      0.125 & 0.052 & 0.039 & 0.039 & 0.039 & 0.039\\
 & La & 0.117 & 0.051 & 0.047 & 0.047 & 0.048 & 0.048 &
      0.117 & 0.048 & 0.043 & 0.043 & 0.043 & 0.042 \\
 & MIX & 0.226 & 0.038 & 0.033 & 0.032 & 0.033 & 0.034 &
      0.225 & 0.029 & 0.031 & 0.032 & 0.034 & 0.035 \\
      \hline
\multirow{3}{*}{KLD} &
EV & 0.171 & 0.025 & 0.014 & 0.013 & 0.014 & 0.015 & 
      0.170 & 0.025 & 0.011 & 0.010 & 0.010 & 0.010\\
& La & 0.110 & 0.014 & 0.012 & 0.012 & 0.012 & 0.012 & 
      0.111 & 0.013 & 0.010 & 0.010 & 0.010 & 0.010 \\
& MIX & 0.221 & 0.010 & 0.008 & 0.008 & 0.009 & 0.010 & 
      0.293 & 0.004 & 0.006 & 0.007 & 0.009 & 0.010
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

%% The amssymb package provides various useful mathematical symbols
% \usepackage{amssymb}
%% The amsmath package provides various useful equation environments.
% \usepackage{amsmath}
\usepackage{amsmath,amsthm,amssymb,scrextend,mathtools}
\usepackage{hyperref}
\usepackage{newtxmath} %for making indicator function
\usepackage{booktabs}
\usepackage{float} %hopefully keeps images and text in order
% \RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,backref=page,backref=page]{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

% \Huge
\begin{center}
  Supplementary Material
\end{center}
\normalsize

\section*{Additional simulation study results to section 4.1}
Figure
\ref{fig:norm_dens} shows examples of marginal
posterior densities for QM of quantiles for a normal distribution from the
simulation study in section 4.1 in
the main manuscript. The parameter uncertainty of the QGP and ORD models are
unsurprisingly similar in
most cases, and where they differ it is hard to say that one is estimating the
true parameter better than the
other. The IND model on the other hand has tighter densities, and often the
bulk of the posterior is far from
the true parameter.

\begin{figure}[hbt!]
\centering
  \includegraphics[width = 1\linewidth]{Images/norm_params_fit.png}
\caption{Density plots of posterior distribution samples for normal parameters 
by QM for QGP, ORD, and
IND models. QM was done on estimated quantiles from a normal distribution with 
mean 4 and standard
deviation 3.5. The posterior densities are for $\mu$ (top left), 
$\sigma$ (top right), and 
sample size n (bottom). Plots are
faceted by the sample size $n \in \{50, 150, 500, 1,000\}$ 
($y$-axis) and number of 
quantiles $K \in \{7, 15, 23\}$ ($x$-axis).
Vertical lines (black) show the value of the true parameter}
\label{fig:norm_dens}
\end{figure}

\newpage
Figures \ref{fig:exp_dens} and \ref{fig:exp_cov_dists} are from a simulation 
study similar to that of section 4.1 
except that QM was performed on
quantiles estimated from draws from an exponential distribution with 
parameter $\lambda = 4$ rather than a normal distribution. 
The results in the study for the exponential distribution were similar 
to those for the normal
distribution.

\begin{figure}[hbt!]
\centering
  \includegraphics[width = 1.1\linewidth]{Images/exp_params_fit.png}
\caption{Density plots of posterior distribution samples for the exponential 
parameters by QM for QGP,
ORD, and IND models. QM was done on estimated quantiles from a exponential 
distribution with parameter
$\lambda = 4$. The posterior densities are for $\lambda$
(left) and sample size $n$ (right). 
Plots are faceted by true sample
size $n \in \{50, 150, 500, 1,000\}$ ($y$-axis) and number of quantiles 
$K \in \{7, 15, 23\}$ 
($x$-axis). Vertical lines (black)
show the value of the true parameter.}
\label{fig:exp_dens}
\end{figure}

@@

\section*{Additional simulation study results to section 4.2}

Figures \ref{fig:lp_fits} and \ref{fig:gmix_fits} show examples of QM fits
to Laplace and normal mixture distributions as described in section 4.2.

@@

\newpage

\section*{QGP normal mixture components analysis}

This section shows an analysis which was made to determine the number of 
normal components to use in the distribution assigned for use in the QGP.
Figure \ref{fig:mix_comps} shows the UWD1, TV, and KLD distances between 
a QGP fit distributions and simulated quantiles averaged over 500 simulated
replicates. Table \ref{tab:mix_comps} shows the average values. The results 
show that while the larger the number of components, the closer is the fit 
distribution in terms of the given distances. However, the imrpovement after 
three or four components is not much making four components attractive 
for relatively good fit and for model simplicity.

\begin{figure}[hbt!]
\centering
  \includegraphics[width=.9\textwidth]{Images/mix_comps.png}
\caption{UWD1, TV, and KLD distances averaged over 500 simulation replicates
for QGP fits of quantile simulated from extreme value, Laplace, and
mixture distributions. The QGP with normal 
mixture distributions of 1 to 6 components were fit for both the cases where 
$n$ is not known (left) and $n$ is known.}
\label{fig:mix_comps}
\end{figure}

\newpage

\begin{table}[hbt!]
\footnotesize
\centering
\caption{UWD1, TV, and KLD distances averaged over 500 simulation replicates
for QGP fits of quantile simulated from extreme value, Laplace, and
mixture distributions. The QGP with normal 
mixture distributions of 1 to 6 components were fit for both the cases where 
$n$ is not known (left) and $n$ is known.}
\begin{adjustbox}{center}
\begin{tabular}{clcccccc|cccccc}
& & \multicolumn{6}{c}{QGP} & \multicolumn{6}{c}{QGP-n} \\
\cmidrule(lr){3-8} \cmidrule(lr){9-14}
& Components & 1 & 2 & 3 & 4 & 5 & 6 & 1 & 2 & 3 & 4 & 5 & 6 \\
\midrule
\multirow{3}{*}{UWD1} &
EV & 0.063 & 0.025 & 0.021 & 0.020 & 0.020 & 0.020 & 
      0.064 & 0.025 & 0.021 & 0.021 & 0.020 & 0.020\\
 & La & 0.044 & 0.022 & 0.020 & 0.020 & 0.020 & 0.020 & 
      0.044 & 0.021 & 0.020 & 0.020 & 0.020 & 0.020 \\
 & MIX & 0.107 & 0.018 & 0.019 & 0.019 & 0.019 & 0.019 & 
      0.157 & 0.018 & 0.019 & 0.018 & 0.018 & 0.018 \\
      \hline
\multirow{3}{*}{TV} &
EV & 0.127 & 0.053 & 0.047 & 0.047 & 0.048 & 0.049 &
      0.125 & 0.052 & 0.039 & 0.039 & 0.039 & 0.039\\
 & La & 0.117 & 0.051 & 0.047 & 0.047 & 0.048 & 0.048 &
      0.117 & 0.048 & 0.043 & 0.043 & 0.043 & 0.042 \\
 & MIX & 0.226 & 0.038 & 0.033 & 0.032 & 0.033 & 0.034 &
      0.225 & 0.029 & 0.031 & 0.032 & 0.034 & 0.035 \\
      \hline
\multirow{3}{*}{KLD} &
EV & 0.171 & 0.025 & 0.014 & 0.013 & 0.014 & 0.015 & 
      0.170 & 0.025 & 0.011 & 0.010 & 0.010 & 0.010\\
& La & 0.110 & 0.014 & 0.012 & 0.012 & 0.012 & 0.012 & 
      0.111 & 0.013 & 0.010 & 0.010 & 0.010 & 0.010 \\
& MIX & 0.221 & 0.010 & 0.008 & 0.008 & 0.009 & 0.010 & 
      0.293 & 0.004 & 0.006 & 0.007 & 0.009 & 0.010
\end{tabular}
\end{adjustbox}
\label{tab:mix_comps}
\end{table}
